AMBIENT; an execution and an MPI-CUDA scheduler

### 2011-08-08 doc/paper_ambient/paper_ambient.tex
minor modifs paper

@@

\subsection{SQL resource management}  \label{SQLSECTION}
 In the previous section, we introduced the logistics kernels and their role in initializing resources for the execution of the computational kernels. 
 One of Ambients' main qualities is the ability to perform a dynamic management of the CPU resources of the cluster. To facilitate this, we integrated a light SQL framework [cite something] inside Ambient, which selects the desired number of processors inside the logistics kernel, in order to execute the computational kernel.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% BEGIN WORKFLOW
\section{Ambient workflow}

Alex, your part !

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% END WORKFLOW

@@

\subsection{SQL resource management}  \label{SQLSECTION}
 In the previous section, we introduced the logistics kernels and their role in initializing resources for the execution of the computational kernels. 
 One of Ambients' main qualities is the ability to perform a dynamic management of the CPU resources of the cluster. To facilitate this, we integrated a light SQL framework \cite{SQLite} inside Ambient, which selects the desired number of processors inside the logistics kernel, in order to execute the computational kernel.
